---
title: "Lab: The 12 Days of Christmas"
output:
  prettydoc::html_pretty:
    theme: tactile
    highlight: github
    css: styles.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Packages for Functions
library(dplyr)
library(glue)
library(stringr)
library(purrr)
```


### A Test Dataset

Run the code below to load up a dataset called `xmas` that contains the crucial 
information about the gifts in the song. We will use this dataset to test out
our functions as we work on them.

```{r}
xmas <- read.csv("https://www.dropbox.com/s/e584pryn8evm1gz/xmas.csv?dl=1")
```

---

## Step One:  Plurals

Note that the gifts are listed in singular: for example, on day five the
narrator receives "five golden rings", but the entry in the dataset for the gift
on day five simply says "ring".  

Using the skeleton of the `pluralize_gift()` function, complete the code so that 
the function takes a gift and returns the appropriate plural. 

**Important:**  You should **absolutely not** "hard-code" anything into this 
function; this function should work in general, not just for the items in the 12 
Days of Christmas.  For example, the word "rings" should not appear anywhere in 
the function.  I should be able to give it any gift and get back the plural of 
that gift.

### Test Your Function

Try your function out on the smaller and then larger gift dataset.  

**Consider: is your function _vectorized_?  It does not have to be, but you can
try it out if you want!**

```{r}
# Function that takes a noun and makes it plural
# Arguments -- gift -- A string or vector of strings
# Return -- A string or vector of strings with the pluralized words

pluralize_gift <- function(gift){

gift <- gift %>%
  str_replace()

return(gift)

}
```

### Test Your Function

Try your function out on the smaller and then larger gift dataset.  

**Consider: is your function _vectorized_?  It does not have to be, but you can
try it out if you want!**

```{r}

pluralize_gift(xmas$Gift.Item)

purrr::map_chr(xmas$Gift.Item, pluralize_gift)

```

---


## Step Two: Creating sentences

Write a function called `make_phrase` that takes as input the necessary information, 
and returns a phrase.  For example, 

```{r}
make_phrase(num = 10, 
            num_word = "ten", 
            item = "lords", 
            verb = "a-leaping", 
            adjective = "", 
            location = "")
```

should return

```
"ten lords a-leaping"
```

```{r}
make_phrase <- function(num, num_word, item, verb, adjective, location) {
  
  ## Step 1: Replace NAs with blank strings
  verb <- str_replace_na(verb, "")
  
  ## Step 2: If the day is larger than 1, the items need pluralized! 
  
  ## Step 3: If the word starts with a vowel, add "an" to the beginning
  
  ## Step 4:" Glue all of the pieces together! 

}
```


### Test Your Function

Try your function out on the `xmas` data, by making a new variable containing 
the daily phrases.

**Hint:** The `Day.in.Words` variable isn't quite what you want! You want `12`
to say `"twelve"` **not** `"twelfth"`. I suggest using the **english** package
to create numbered days and then use those in your `pmap_chr()`!


```{r}
xmas2 <- xmas %>%
  mutate(day.num = as.character(english::english(Day)
                                ), 
    Full.Phrase = pmap_chr(
      list(num = Day,
           num_word = day.num,
           item = Gift.Item,
           verb = Verb,
           adjective = Adjective,
           location = Location),
      make_phrase
      )
  )
```


**Your `Full.Phrase` column is the answer to this week's Practice Activity.**

**Copy and paste your `Full.Phrase` column to show me the phrases you made!**

---

## Challenge: Final Step -- Iteration

Write a function called `sing_line()` that takes as input:

* A dataset

* A number indicating which day to sing about

* The name of a column in the dataset that contains the phrases for each day.

For example,

```{r}
sing_line(xmas, 2, Full.Phrase)
```

should return

```
On the second day of Christmas, my true love sent to me:
two turtle doves and
a partridge in a pear tree.
```

*Hint:*  The `{{ phrase_col }}` part, which I provided for you, lets you use 
column names as arguments to a function.  Don't delete that line of code!

```{r}
# Produces the string for one day of the song.
# Arguments -- dataset -- A data frame containing information about gifts
# Arguments -- line -- The number of the line for the day you want to sing about
# Arguments -- phrase_col -- The variable name for the column in the dataset that contains the gift phrases
# Return -- A string singing the line of the song with all gifts for the given day.

sing_day <- function(dataset, line, phrase_col){
  
  # Step 1: Setup the intro line
  
  num_word <- ____
  
  intro <- glue::glue("On the {num_word} day of Christmas")
  
  # Step 2: Sing the gift phrases

    phrases <- dataset %>% 
      pull( {{phrase_col}} )

  ????
    
  ## put it together
    
  ????

}

```

### A Small Test

```{r}
xmas %>% 
sing_line(num = 2, phrase_col = Full.Phrase)

```

### A Larger Test

```{r}
map_chr(1:12, ~ sing_line(xmas2, .x, Full.Phrase)) %>%
  str_c(collapse = "\n") %>%
  cat()

```

