---
title: "Lab: The 12 Days of Christmas"
author: "Zuhayr Baqar, Dan Ngyuyen, Rachel Roggenkemper, Annie Zell (Group 5)"
output:
  prettydoc::html_pretty:
    theme: tactile
    highlight: github
    css: styles.css
---

<style>
div.blue { background-color:#e6f0ff; border-radius: 5px; padding: 10px;}
</style>
<div class = "blue">

Great work! You have no revisions! 

You defined the `make_phrase()` function twice. While this does not produce 
extraneous output, this could cause **major** issues if the functions are 
different! I am deducting 1 point from your overall score for this oversight. 

**Score** (average score for 7 questions): 3.714

</div>

```{r setup, include = FALSE, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Packages for Functions
library(dplyr)
library(glue)
library(stringr)
library(purrr)
library(english)
```


### A Test Dataset

Run the code below to load up a dataset called `xmas` that contains the crucial 
information about the gifts in the song. We will use this dataset to test out
our functions as we work on them.

```{r}
xmas <- read.csv("https://www.dropbox.com/s/e584pryn8evm1gz/xmas.csv?dl=1")
```

---

## Step One:  Plurals

Note that the gifts are listed in singular: for example, on day five the
narrator receives "five golden rings", but the entry in the dataset for the gift
on day 5 simply says "ring".  

Using the skeleton of the `pluralize_gift()` function, complete the code so that 
the function takes a gift and returns the appropriate plural. 

```{r, message = FALSE, warning = FALSE}
# Function that takes a noun and makes it plural
# Arguments -- gift -- A string or vector of strings
# Return -- A string or vector of strings with the pluralized words

pluralize_gift <- function(gift){
if (str_detect(gift, "oo"))  {
gift <- gift %>%
  str_replace("oo", "ee")
} else if(str_detect(gift, "y$")){
  gift <- gift %>%
  str_replace("y$", "ies")
} else {
  gift <- glue::glue("{gift}s")
}
return(gift)
}

```

<style>
div.blue { background-color:#e6f0ff; border-radius: 5px; padding: 10px;}
</style>
<div class = "blue">

Nice work `glue()`-ing the "s" on the end! I also appreciate how you indicated 
that the "y" needed to come at the end of the word! 

**4**

</div>

*Hint 1:* Note that the gifts on days six and nine have unusual pluralizations.
You may assume that in other datasets, there will be no special cases besides
these types.

*Hint 2:*  The following small example may be useful to you:

```{r, message = FALSE, warning = FALSE}
my_names <- c("Kimberly", "Trini", "Jason", "Billy", "Zach", "Tommy")

my_names %>% 
  str_replace("y$", "ies")
```


**Important:**  You should **absolutely not** "hard-code" anything into this 
function; this function should work in general, not just for the items in the
12 Days of Christmas.  For example, the word "rings" should not appear anywhere
in the function.  I should be able to give it any gift and any day, and get back
the plural of that gift.


### Test Your Function

Try your function out on the gifts in the dataset.  
(Consider: is your function *vectorized*?  It does not have to be, but it may
make things simpler!)

```{r, message = FALSE, warning = FALSE}

pluralize_gift(xmas$Gift.Item)

purrr::map_chr(xmas$Gift.Item, pluralize_gift)

```

<style>
div.blue { background-color:#e6f0ff; border-radius: 5px; padding: 10px;}
</style>
<div class = "blue">

**4** -- Nice! Does your function need `map_chr()` to be used on a vector? 

</div>

---


## Step Two: Creating sentences

Write a function called `make_phrase` that takes as input the necessary information, 
and returns a phrase.  

```{r, message = FALSE, warning = FALSE}
make_phrase <- function(num, num_word, item, verb, adjective, location) {
  
  ## Step 1: Replace NAs with blank strings
  verb <- str_replace_na(verb, "")
  location <- str_replace_na(location, "")
  adjective <- str_replace_na(adjective, "")
  
  ## Step 2: Pluralize the gift if needed
  ## Items with numbers larger than 1 should be pluralized
  ## Single items starting with a vowel should have "an" in front
  ## All other single items should have "a" in front
  
  vowel_start <- str_sub(item, 1, 1) %>% str_detect("[aeiou]")
  
  if (num > 1) {
    
    item <- pluralize_gift(item)
      num_word <- as.english(num)
    
  } else if (vowel_start) {
  
      num_word <- "an"
    
  } else {
    
    num_word <- "a"
    
  }
  
  return(glue::glue("{num_word} {adjective} {item} {verb} {location}") %>%
    str_squish())
  
  
}
```

<style>
div.blue { background-color:#e6f0ff; border-radius: 5px; padding: 10px;}
</style>
<div class = "blue">

**4** -- Nice cases! 

</div>


```{r, message = FALSE, warning = FALSE}
make_phrase(num = 10, 
            num_word = "ten", 
            item = "lord", 
            verb = "a-leaping", 
            adjective = "", 
            location = "")
```

<style>
div.blue { background-color:#e6f0ff; border-radius: 5px; padding: 10px;}
</style>
<div class = "blue">

**4** -- Great work! 

</div>


```{r, message = FALSE, warning = FALSE}
make_phrase <- function(num, num_word, item, verb, adjective, location) {
  
  ## Step 1: Replace NAs with blank strings
  verb <- str_replace_na(verb, "")
  location <- str_replace_na(location, "")
  adjective <- str_replace_na(adjective, "")
  
  ## Step 2: Pluralize the gift if needed
  ## Items with numbers larger than 1 should be pluralized
  ## Single items starting with a vowel should have "an" in front
  ## All other single items should have "a" in front
  
  vowel_start <- str_sub(item, 1, 1) %>% str_detect("[aeiou]")
  
  if (num > 1) {
    
    item <- pluralize_gift(item)
      num_word <- as.english(num)
    
  } else if (vowel_start) {
  
      num_word <- "an"
    
  } else {
    
    num_word <- "a"
    
  }

  
  return(glue::glue("{num_word} {adjective} {item} {verb} {location}") %>%
    str_squish())
  
  
}
```

<style>
div.blue { background-color:#e6f0ff; border-radius: 5px; padding: 10px;}
</style>
<div class = "blue">

**You already defined this function!**

</div>



# Test Your Function

Try your function out on the `xmas` data, by making a new variable containing
the daily phrases.

**Hint:** The `Day.in.Words` variable isn't quite what you want! You want `12`
to say `"twelve"` **not** `"twelfth"`. I suggest using the **english** package
to create numbered days and then use those in your `pmap_chr()`!

```{r, message = FALSE, warning = FALSE}
#Test function: 
xmas <- xmas %>%
  mutate(day.num = as.english(Day),
    Full.Phrase = pmap_chr(list(num = Day, 
                                num_word = as.english(Day), 
                                item = Gift.Item, 
                                verb = Verb, 
                                adjective = Adjective, 
                                location = Location), 
                           make_phrase))

```

<style>
div.blue { background-color:#e6f0ff; border-radius: 5px; padding: 10px;}
</style>
<div class = "blue">

**4** -- Great! 

</div>

---


## Step Three:  Iteration.

Write a function called `sing_line` that takes as input:

* A dataset

* A number indicating which day to sing about

* The name of a column in the dataset that contains the phrases for each day.

```{r, message = FALSE, warning = FALSE}
# Produces the string for one day of the song.
# Arguments -- dataset -- A data frame containing information about gifts
# Arguments -- line -- The number of the line for the day you want to sing about
# Arguments -- phrase_col -- The variable name for the column in the dataset that contains the gift phrases
# Return -- A string singing the line of the song with all gifts for the given day.
sing_line <- function(dataset, line, phrase_col){
  
  # Step 1: Setup the intro line
  
  num_word <- dataset$Day.in.Words
  
  intro <- glue::glue("On the {num_word} day of Christmas, my true love sent to me:")
  
  # Step 2: Sing the gift phrases
    phrases <- dataset %>% 
      pull({{phrase_col}})
    
    until_two <- paste0(glue::glue("{phrases[line:2]}"), collapse = "\n")
    
    last <- glue::glue("and {phrases[1]}")
    
    one <- glue::glue("{phrases[1]}")
    
    full_phrase <- glue::glue("{intro[line]} \n{until_two} \n{last}.")
      
  if(line == 1){
    return(glue::glue("{intro[line]} \n{one}."))
    
  } else{
  return(full_phrase)    
  }
}
```

<style>
div.blue { background-color:#e6f0ff; border-radius: 5px; padding: 10px;}
</style>
<div class = "blue">

**3** -- Your function assumes that there is a `Day.in.Words` variable in the 
dataset. I had hoped that if you intended to use this variable, you would have
extracted it in a similar way to the `phrase_col`. Does the intro phrase need 
to be repeated? It seems like you just extract the `line` number of the `intro`
that you want, so why make all 12 lines?

</div>

For example,


```{r, message = FALSE, warning = FALSE}
sing_line(xmas, 
          line = 2, 
          phrase_col = Full.Phrase)

```

<style>
div.blue { background-color:#e6f0ff; border-radius: 5px; padding: 10px;}
</style>
<div class = "blue">

**4** -- Nice work!

</div>

should return

```
On the second day of Christmas, my true love sent to me,
two turtle doves 
and a partridge in a pear tree.
```

*Hint:*  The `{{phrase_col}}` part, which I provided for you, lets you use 
column names as arguments to a function.  Don't delete that line of code!

---

## Step Four: Use Your Functions!

Run the following code to test out your functions! The ouput should be the 
lyrics for the entire 12 Days of Christmas song. 

```{r, message = FALSE, warning = FALSE}
xmas2 <- xmas %>%
  mutate(
    day.num = as.character(english::english(Day)), 
    Full.Phrase = pmap_chr(list(num = Day, 
                                num_word = day.num, 
                                item = Gift.Item, 
                                verb = Verb, 
                                adjective = Adjective, 
                                location = Location), 
                           make_phrase)
  )
map_chr(1:12, ~sing_line(xmas2, .x, Full.Phrase)) %>%
  str_c(collapse = "\n") %>%
  cat()

```

<style>
div.blue { background-color:#e6f0ff; border-radius: 5px; padding: 10px;}
</style>
<div class = "blue">

**4** -- Nice work! I like how each gift has its own line! 

</div>

Citation: Rachel's older brother- paste0

<style>
div.blue { background-color:#e6f0ff; border-radius: 5px; padding: 10px;}
</style>
<div class = "blue">

`paste0()` does the same thing as `str_c()`!!!

</div>


